---
title: "Anti-Trust Data Scrape"
author: "Tyler Mallon"
date: "June 3, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary of Contents

This notebook scrapes anti-trust case data from [this](https://www.justice.gov/atr/antitrust-case-filings-alpha) location. It then creates a structured dataset of the contents found from each of the individual case files. This data isn't perfectly cleaned, but rather is reflective of what can be found directly from the source. We have taken some minor effort to place this data in a flat file, but this could benefit from further cleaning. The code chunks are broken out between the scraping function and the cleaning efforts.  

```{r pkg_loag, eval = FALSE}
rm(list=ls(all=T))
library(tidyverse)
library(rvest)
```

## Scrape

```{r scrape_code, eval = FALSE}
# appropriate css selectors determined using SelectorGadget chrome plugin

caselinkcss <- ".even div p a"
datavalcss <- ".field--label-above .odd , .field--label-above .even , .date-display-single , .field__label"

get_case_data <- function(baseurl, caselinkcss, datavalcss) {
  
  # get character vector of links to click on
  case_filings <- read_html(baseurl) %>%
    html_nodes(caselinkcss) %>%
    html_text()
  
  # begin headless browser
  session <- html_session(baseurl)
  
  #initialize empty list
  lyst <- list()

  # iterate through character vector of list links and jump into each one, extract out the data values as a vector and store in a list
  for (i in 1:length(case_filings)) {
   lyst[[i]] <- session %>%
    follow_link(case_filings[i]) %>%
      html_nodes(datavalcss) %>%
      html_text(trim = TRUE) %>%
      unique(.)
  }
  
  # name list elements by link string
  names(lyst) <- case_filings
  
  # collapse all character vectors into a dataframe
  df <- enframe(lyst) %>% # creates the 'value' as a `list` column
   mutate(value = map(value, as.character)) %>% # change to single type
   unnest(.) %>%
    mutate(index = seq_along(name))
  
  # label rows as key or value based on colon.
  df <- df %>%
  mutate(kv = ifelse(value %>% str_detect(":"), "Key", "Value"))
  
  # initialize empty list
  lyst2 <- list()

  # loop through df and extract out the index of keys
  for (i in 1:length(df$index) + 1) {
    lyst2[i] <- tail(which(df$index < i & df$kv == "Key"), n = 1L)
  }
  
  # remove first list element since it's null
  lyst2[[1]] <- NULL
  
  # turn lyst2 into a dataframe
  lyst2 <- unlist(lyst2) %>%
  enframe(., value = "index", name = NULL)
  
  # join key column on df
  df <- df %>%
  select(value, index) %>%
  right_join(lyst2, by = "index") %>%
  select(value) %>%
  rename("Key" = value) %>%
  bind_cols(., df) %>%
  filter(kv == "Value") %>%
  select(Key, name, value)
  
  return(df)
}

# run scrape
case_data <- get_case_data(baseurl = "https://www.justice.gov/atr/antitrust-case-filings-alpha", 
              caselinkcss = ".even div p a",
              datavalcss = ".field--label-above .odd , .field--label-above .even , .date-display-single , .field__label")

# write scraped data
write_csv(case_data, "anti_trust_case_data.csv")
```

## Clean

```{r clean_code, eval = FALSE}
# read scraped data
anti_trust <- read_csv("anti_trust_case_data.csv")

# remove unnecessary colons
anti_trust <- anti_trust %>%
  mutate(Key = str_replace(Key,":",""))

# look for all key values
key_list <- anti_trust %>%
  distinct(Key)

# select only generic key values
anti_trust <- anti_trust %>%
  filter(Key %in% c("Case Open Date", "Case Name", "Case Type", "Case Violation", "Market", "Industry Code", "Component", "Topic")) %>%
  distinct(Key, name, value)
 
# create flat file of data
anti_trust_flat <- anti_trust %>%
  group_by(Key, name) %>%
  mutate(ind = row_number()) %>%
  spread(Key, value) %>%
  ungroup(.) %>%
  group_by(name) %>%
  select(everything(), -ind) %>%
  fill(everything(), .direction = c("down")) %>%
  rename("Link Title" = name)

write_csv(anti_trust_flat, "anti_trust_spread.csv", append = FALSE)
```